Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-08 volunteer-clouds-ieee-ci-si.tex
Added intro to Nodio-WW section
Please @mariosky check that it is correct.

>>>>

In order to improve the number of cycles per user, we improved the
basic architecture in several different aspects. By using WebWorkers
the algorithm kept running on the background even if the {\sf NodIO}
tab was not in focus. It also allowed to run several clients per
browser, as opposed to a single one as we did previously. Another
improvement involved restart of the client once the solution was
found, so that as long as the user was visiting the page it was
running an evolutionary algorithm. Finally, a small algorithmic
improvement was included: instead of having a fixed population,
population size was random and different for each client.
